Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-10 cmsb22.tex
Original models and BioLQM transformation to bnet

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes. Number in bold indicate a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $e$ & $s$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem & 9 &&& 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate & 28 &&& 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma & 23 &&& 32 & 0.04 & 0.11\\
    davidich\_yeast & 10 &&& 12 & 0.03 & 0.08\\
    dinwoodie\_life & 15 &&& 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal & 13 &&& 1 & 0.04 & 0.05\\
    faure\_cellcycle & 10 &&& 2 & 0.04 & 0.04\\
    grieco\_mapk & 53 &&& 18 & 0.04 & 0.08\\
    irons\_yeast & 18 &&& 1 & 0.05 & 0.04\\
    jaoude\_thdiff & 103 &&& 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr & 40 &&& 8 & 0.06 & 0.04\\
    krumsiek\_myeloid & 11 &&& 6 & 0.03 & 0.03\\
    multivalued & 13 &&& 4 & 0.02 & 0.02\\
    n12c5 & 11 &&& 5 & \textbf{34.37} & 0.06\\
    n3s1c1a & 2 &&& 2 & 0.02 & 0.03\\
    n3s1c1b & 2 &&& 2 & 0.02 & 0.03\\
    n5s3 & 4 &&& 3 & 0.03 & 0.03\\
    n6s1c2 & 5 &&& 3 & 0.03 & 0.04\\
    n7s3 & 6 &&& 3 & 0.02 & 0.02\\
    raf & 3 &&& 2 & 0.03 & 0.02\\
    randomnet\_n15k3 & 15 &&& 3 & 0.04 & 0.05\\
    randomnet\_n7k3 & 7 &&& 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis & 34 &&& 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell & 13 &&& 1 & 0.02 & 0.03\\
    selvaggio\_emt & 56 &&& 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis & 12 &&& 3 & 0.05 & 0.06\\
    xiao\_wnt5a & 7 &&& 4 & 0.06 & 0.03\\
    zhang\_tlgl & 60 &&& 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 & 60 &&& 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}
\end{table}

  \sylvain{I'm not sure that \(e\) and \(s\) are very relevant, moreover they are not readily available\dots}
  \vangiang{Indeed, they are not readily available. But if we use more meaningful words, the width of the table may exceed the width of the page. Thus, I use \(e\) and \(s\) along with the explanations shown in the table's caption. Do you have any other option?}

@@

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $e$ & $s$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    CASCADE3 & 183 &&& 1 & 82.86 & 12.83\\
    KYNURENINE-PATHWAY & 150 &&& 1000+ & 74.71 & 4.22\\
    SN5 & 2746 &&& ??? & DNF & DNF\\
    ERBB-RECEPTOR-SIGNALING & 247 &&& 1000+ & DNF & 9.27\\
    Executable\_file\_for\_cholocystokinin\_model & 404 &&& 1000+ & 1.55 & 3.57\\
    korkut\_2015a & 99 &&& 1000+ & DNF & 3.06\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 &&& 1000+ & 0.43 & 0.66\\
    Corral\_ThIL17diff\_15jan2021 & 92 &&& 1000+ & DNF & 0.91\\
    HIV-1 & 138 &&& 1000+ & DNF & 3.25\\
    Executable\_file\_for\_CaSQ\_derived\_mast\_cell\_activation\_model & 80 &&& 1000+ & 0.49 & 0.56\\
    Colitis\_associated\_colon\_cancer & 70 &&& 10 & 0.15 & 0.22\\
    INTERFERON-1 & 121 &&& 1000+ & 7.69 & 1.05\\
    TLGLSurvival & 61 &&& 318 & 0.59 & 0.48\\
    cho\_2016\_all\_pos & 200 &&& 1000+ & DNF & 3.00\\
    turei\_2016 & 4691 &&& ??? & DNF & DNF\\
    Human\_network & 1953 &&& 1000+ & DNF & DNF\\
    Executable\_file\_for\_CaSQ\_derived\_MAPK\_model & 182 &&& 1000+ & 75.32 & 2.26\\
    TCR-TLR5-SIGNALING-2018 & 130 &&& 48 & 0.93 & 0.53\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 &&& 1000+ & 36.21 & 2.27\\
    IMMUNE-SYSTEM & 164 &&& 1000+ & DNF & 2.78\\
    HMOX1-PATHWAY & 145 &&& 1000+ & 3.89 & 0.95\\
    Signaling\_in\_Macrophage\_Activation & 321 &&& 1000+ & 11.51 & 3.27\\
    FIBROBLASTS & 139 &&& 1000+ & DNF & 1.91\\
    S1\_Table & 1659 &&& 1000+ & DNF & DNF\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 &&& 78 & 40.59 & 2.15\\
    SIGNALING-IN-PROSTATE-CANCER & 133 &&& 1000+ & DNF & 1.70\\
    InflammatoryBowelDisease & 47 &&& 1 & DNF & 118.78\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 &&& 1000+ & 47.69 & 0.87\\
    IL\_6\_Signalling & 86 &&& 1000+ & 1.10 & 0.46\\
    VIRUS-REPLICATION-CYCLE & 154 &&& 1000+ & DNF & 1.16\\
    Executable\_file\_for\_Alzheimer\_model & 1169 &&& 1000+ & DNF & 6.15\\
    ER-STRESS & 182 &&& 1000+ & 16.15 & 0.93\\
    RA\_apoptosis\_executable\_module & 180 &&& 1000+ & DNF & 0.96\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Column "\(n\)" denotes the numbers of nodes of each model. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes. Number in bold indicate a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem & 9 & 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate & 28 & 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma & 23 & 32 & 0.04 & 0.11\\
    davidich\_yeast & 10 & 12 & 0.03 & 0.08\\
    dinwoodie\_life & 15 & 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal & 13 & 1 & 0.04 & 0.05\\
    faure\_cellcycle & 10 & 2 & 0.04 & 0.04\\
    grieco\_mapk & 53 & 18 & 0.04 & 0.08\\
    irons\_yeast & 18 & 1 & 0.05 & 0.04\\
    jaoude\_thdiff & 103 & 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr & 40 & 8 & 0.06 & 0.04\\
    krumsiek\_myeloid & 11 & 6 & 0.03 & 0.03\\
    multivalued & 13 & 4 & 0.02 & 0.02\\
    n12c5 & 11 & 5 & \textbf{34.37} & 0.06\\
    n3s1c1a & 2 & 2 & 0.02 & 0.03\\
    n3s1c1b & 2 & 2 & 0.02 & 0.03\\
    n5s3 & 4 & 3 & 0.03 & 0.03\\
    n6s1c2 & 5 & 3 & 0.03 & 0.04\\
    n7s3 & 6 & 3 & 0.02 & 0.02\\
    raf & 3 & 2 & 0.03 & 0.02\\
    randomnet\_n15k3 & 15 & 3 & 0.04 & 0.05\\
    randomnet\_n7k3 & 7 & 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis & 34 & 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell & 13 & 1 & 0.02 & 0.03\\
    selvaggio\_emt & 56 & 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis & 12 & 3 & 0.05 & 0.06\\
    xiao\_wnt5a & 7 & 4 & 0.06 & 0.03\\
    zhang\_tlgl & 60 & 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 & 60 & 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}
\end{table}

  \sylvain{I'm not sure that \(e\) and \(s\) are very relevant, moreover they are not readily available\dots}
  \vangiang{Indeed, they are not readily available. But if we use more meaningful words, the width of the table may exceed the width of the page. Thus, I use \(e\) and \(s\) along with the explanations shown in the table's caption. Do you have any other option?}
  \sylvain{just remove them since they are not relevant}

@@

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns "\(n\)" denotes the numbers of nodes of each model. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    CASCADE3 & 183 & 1 & 82.86 & 12.83\\
    KYNURENINE-PATHWAY & 150 & 1000+ & 74.71 & 4.22\\
    SN5 & 2746 & ??? & DNF & DNF\\
    ERBB-RECEPTOR-SIGNALING & 247 & 1000+ & DNF & 9.27\\
    Executable\_file\_for\_cholocystokinin\_model & 404 & 1000+ & 1.55 & 3.57\\
    korkut\_2015a & 99 & 1000+ & DNF & 3.06\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 & 1000+ & 0.43 & 0.66\\
    Corral\_ThIL17diff\_15jan2021 & 92 & 1000+ & DNF & 0.91\\
    HIV-1 & 138 & 1000+ & DNF & 3.25\\
    Executable\_file\_for\_CaSQ\_derived\_mast\_cell\_activation\_model & 80 & 1000+ & 0.49 & 0.56\\
    Colitis\_associated\_colon\_cancer & 70 & 10 & 0.15 & 0.22\\
    INTERFERON-1 & 121 & 1000+ & 7.69 & 1.05\\
    TLGLSurvival & 61 & 318 & 0.59 & 0.48\\
    cho\_2016\_all\_pos & 200 & 1000+ & DNF & 3.00\\
    turei\_2016 & 4691 & ??? & DNF & DNF\\
    Human\_network & 1953 & 1000+ & DNF & DNF\\
    Executable\_file\_for\_CaSQ\_derived\_MAPK\_model & 182 & 1000+ & 75.32 & 2.26\\
    TCR-TLR5-SIGNALING-2018 & 130 & 48 & 0.93 & 0.53\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 & 1000+ & 36.21 & 2.27\\
    IMMUNE-SYSTEM & 164 & 1000+ & DNF & 2.78\\
    HMOX1-PATHWAY & 145 & 1000+ & 3.89 & 0.95\\
    Signaling\_in\_Macrophage\_Activation & 321 & 1000+ & 11.51 & 3.27\\
    FIBROBLASTS & 139 & 1000+ & DNF & 1.91\\
    S1\_Table & 1659 & 1000+ & DNF & DNF\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 & 78 & 40.59 & 2.15\\
    SIGNALING-IN-PROSTATE-CANCER & 133 & 1000+ & DNF & 1.70\\
    InflammatoryBowelDisease & 47 & 1 & DNF & 118.78\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 & 1000+ & 47.69 & 0.87\\
    IL\_6\_Signalling & 86 & 1000+ & 1.10 & 0.46\\
    VIRUS-REPLICATION-CYCLE & 154 & 1000+ & DNF & 1.16\\
    Executable\_file\_for\_Alzheimer\_model & 1169 & 1000+ & DNF & 6.15\\
    ER-STRESS & 182 & 1000+ & 16.15 & 0.93\\
    RA\_apoptosis\_executable\_module & 180 & 1000+ & DNF & 0.96\\
    \bottomrule
  \end{tabular}
\end{table}
